---
title: "Four Parameters:Categorical"
author: "Gitanjali Sheth"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: FALSE

library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)

```

```{r}
#| label: cleaning
#| message: FALSE

nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot"
  ))
```

```{r}
#| label: model
#| cache: true

fit_nes <- brm(formula = pres_vote ~ sex,
               data = nes_92,
               family = categorical(),
               silent = 2,
               refresh = 0,
               seed = 76)
```



```{r}
#| label: plot
ndata <- tibble(sex = c("Female", "Male"))

fit_nes |> add_epred_draws(newdata = ndata) |>
  select(sex, .category, .epred) |>
  ggplot(aes(x = .epred, fill = sex)) +
  geom_histogram(bins = 100) +
  facet_grid(~ .category) +
  scale_x_continuous(breaks = c(0.05, 0.3, 0.6), labels = scales::percent_format()) +
  labs(title="Posterior for Expected Probability of Candidate Support Among Women", subtitle="Women are most likely to support Clinton", x="Posterior Probability of Expected Vote Probability")
```
Using data from the National Election Studies (NES) survey of US citizens, we seek to understand the relationship between voter preference and sex in the 1992 Presidential election. Our results might be biased by differential non-response among different categories of voters. We modeled pres_vote, a character variable, as a multinomial logistic regression model. Women are most likely to support Clinton. About 53% of women claim to support Clinton, although that number could be as high as 58% or as low as 48%.


\begin{aligned}
\rho_{clinton} &=& \frac{e^{\beta_{0, clinton} + \beta_{1, clinton} male}}{1 + e^{\beta_{0, clinton} + \beta_{1, clinton} male}}\\
\rho_{perot} &=& \frac{e^{\beta_{0, perot} + \beta_{1, perot} male}}{1 + e^{\beta_{0, perot} + \beta_{1, perot} male}}\\
\rho_{bush}  &=& 1 - \rho_{clinton} - \rho_{perot}
\end{aligned}

```{r}
#| label: table

tbl_regression(fit_nes)
```